### 2022-07-05 manuscript.tex
Merge pull request #249 from SORTEE-Github-Hackathon/hypothesis_EJH [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/fa53fc1f6968dfcec7f638e637a738b8da99085a.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/fa53fc1f6968dfcec7f638e637a738b8da99085a/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2618260413

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/366e2cb6517a7428a3aacf57613b727b67c17a03/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/366e2cb6517a7428a3aacf57613b727b67c17a03}{SORTEE-Github-Hackathon/manuscript@366e2cb}
on July 5, 2022.

@@

In this paper, we described twelve ways that EEB researchers can leverage GitHub to enable more transparent and collaborative research (Figure \ref{fig:scatterblob}).
Many of the examples are specifically meant for first-time GitHub users and can likely be adopted with just a little practice (storing data, creating virtual notebooks, making code citable).
For example, storing code and data and making it citable involve creating a repository on GitHub, pushing code to the repository, and then going through the necessary steps (\emph{e.g.}, connecting a GitHub repository with Zenodo; see below) for creating a DOI.
These actions are often covered in GitHub tutorials and require little effort to implement.
On the other hand, some examples we described here, including course material development, web hosting, and delivery, may require a greater time commitment, but have the potential to make EEB research more open, accessible, and collaborative.
Managing full research projects or laboratories on GitHub require careful thought as to how to delegate tasks such as reviewing pull requests or creating issues.
For example, collaboratively writing a paper using GitHub, as we have done here, may involve a learning curve for co-authors less familiar with the intricacies of GitHub, and requires overhead to set up the repository using GitHub Actions.
Despite the many potential applications of GitHub to EEB research, we acknowledge that there will still be many times when researchers might look to other platforms for research collaboration.

@@

First, real-time collaborative editing of files is not possible in GitHub.
Users seeking to real-time edit documents might still need to rely on alternative features (\emph{e.g.}, cloud-stored documents from Microsoft Word, Google Docs, hackMD (\url{https://hackmd.io/})).
Second, certain operations that are dependent on other software might not be easily achievable in GitHub, such as manipulating figures or tables.
Although creating tables and figures can be achieve through code, users may be limited to other software to collaboratively brainstorm figures and tables (e.g.~Google Slides, Google Sheets).
Albeit, files containing documents, figures and tables may still be versioned in GitHub.

@@

First, there may be hesitation to independently adopting and learning a new tool.
Institutional encouragement and instructional resources focused in researchers in ecology and evolution may be limited.
When GitHub is taught within an EEB context, it is usually accompanying coursework in topics such as statistical programming.
It can be challenging to learn Git alongside scripting languages, statistical theory, and file system navigation, especially when many may be inexperimented with programming.
Instructors likewise may confuse the expected digital literacy of students with computational fluency, even when modern technology increasingly abstracts concepts through search optimization and preponderant integrated development environments (IDE), or `point-and-click' user interfaces.

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/fa53fc1f6968dfcec7f638e637a738b8da99085a/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/fa53fc1f6968dfcec7f638e637a738b8da99085a}{SORTEE-Github-Hackathon/manuscript@fa53fc1}
on July 5, 2022.

@@

In this paper, we described twelve ways that EEB researchers can leverage GitHub to enable more transparent and collaborative research (Figure \ref{fig:scatterblob}).
Many of the examples are specifically meant for first-time GitHub users and can likely be adopted with just a little practice (storing data, creating virtual notebooks, making code citable).
For example, storing code and data and making it citable involve creating a repository on GitHub, pushing code to the repository, and then going through the necessary steps (\emph{e.g.}, connecting a GitHub repository with Zenodo; see below) for creating a DOI.
These actions are often covered in GitHub tutorials and require little effort to implement.
On the other hand, some examples we described here, including course material development, web hosting, and delivery, may require a greater time commitment, but have the potential to make EEB research more open, accessible, and collaborative.
Managing full research projects or laboratories on GitHub requires careful thought as to how to delegate tasks such as reviewing pull requests or creating issues.
For example, collaboratively writing a paper using GitHub, as we have done here, may involve a learning curve for co-authors less familiar with the intricacies of GitHub, and requires overhead to set up the repository using GitHub Actions.
Despite the many potential applications of GitHub to EEB research, we acknowledge that there will still be many times when researchers might look to other platforms for research collaboration.

@@

First, real-time collaborative editing of files is not possible in GitHub.
Users seeking to real-time edit documents might still need to rely on alternative features (\emph{e.g.}, cloud-stored documents from Microsoft Word, Google Docs, hackMD (\url{https://hackmd.io/})).
Second, certain operations that are dependent on other software might not be easily achievable in GitHub, such as manipulating figures or tables.
Although creating tables and figures can be achieved through code, users may be limited to other software to collaboratively brainstorm figures and tables (e.g.~Google Slides, Google Sheets).
Albeit, files containing documents, figures and tables may still be versioned in GitHub.

@@

First, there may be hesitation to independently adopting and learning a new tool.
Institutional encouragement and instructional resources focused on researchers in ecology and evolution may be limited.
When GitHub is taught within an EEB context, it is usually accompanying coursework in topics such as statistical programming.
It can be challenging to learn Git alongside scripting languages, statistical theory, and file system navigation, especially when many may be inexperienced with programming.
Instructors likewise may confuse the expected digital literacy of students with computational fluency, even when modern technology increasingly abstracts concepts through search optimization and preponderant integrated development environments (IDE), or `point-and-click' user interfaces.
